\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-01-29 papers/jss/article.Rnw
typo
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@868 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

%% an abstract and keywords
\Abstract{
Modern data collection and analysis pipelines often involve
a sophisticated mix of applications written in general purpose and
specialized programming languages.  
Many formats commonly used to import and export data between
different programs or systems, such as \texttt{CSV} or \texttt{JSON}, are
verbose, inefficient, not type-safe, or tied to a specific programming language.
Protocol Buffers are a popular
method of serializing structured data between applications---while remaining
independent of programming languages or operating systems.
They offer a unique combination of features, performance, and maturity that seems
particulary well suited for data-driven applications and numerical
computing.
The
\CRANpkg{RProtoBuf} package provides a complete interface to Protocol
Buffers from the
\proglang{R} environment for statistical computing.
This paper outlines the general class of data serialization
requirements for statistical computing, describes the implementation
of the \CRANpkg{RProtoBuf} package, and illustrates its use with
example applications in large-scale data collection pipelines and web
services.
%TODO(ms) keep it less than 150 words. -- I think this may be 154,
%depending how emacs is counting.
}
\Keywords{\proglang{R}, \pkg{Rcpp}, Protocol Buffers, serialization, cross-platform}
\Plainkeywords{R, Rcpp, Protocol Buffers, serialization, cross-platform} %% without formatting
%% at least one keyword must be supplied

>>>>

%% an abstract and keywords
\Abstract{
Modern data collection and analysis pipelines often involve
a sophisticated mix of applications written in general purpose and
specialized programming languages.  
Many formats commonly used to import and export data between
different programs or systems, such as \texttt{CSV} or \texttt{JSON}, are
verbose, inefficient, not type-safe, or tied to a specific programming language.
Protocol Buffers are a popular
method of serializing structured data between applications---while remaining
independent of programming languages or operating systems.
They offer a unique combination of features, performance, and maturity that seems
particularly well suited for data-driven applications and numerical
computing.
The
\CRANpkg{RProtoBuf} package provides a complete interface to Protocol
Buffers from the
\proglang{R} environment for statistical computing.
This paper outlines the general class of data serialization
requirements for statistical computing, describes the implementation
of the \CRANpkg{RProtoBuf} package, and illustrates its use with
example applications in large-scale data collection pipelines and web
services.
%TODO(ms) keep it less than 150 words. -- I think this may be 154,
%depending how emacs is counting.
}
\Keywords{\proglang{R}, \pkg{Rcpp}, Protocol Buffers, serialization, cross-platform}
\Plainkeywords{R, Rcpp, Protocol Buffers, serialization, cross-platform} %% without formatting
%% at least one keyword must be supplied
